---
title: My dynamic report
output: html_fragment
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)
library(tidyverse)
```
```{css}
@import url('https://fonts.googleapis.com/css2?family=Playfair+Display:wght@600&family=Lato:wght@300;400&display=swap');

body {
  font-family: 'Lato', sans-serif;
  font-weight: 300;
  font-size: 13pt;
  color: #2c2c2c;
  background-color: #fdf6f0;
  max-width: 860px;
  margin: auto;
  padding: 30px;
}

h2 {
  font-family: 'Playfair Display', serif;
  color: #7b4f6e;
  text-align: center;
  font-size: 2em;
}

h3 {
  font-family: 'Playfair Display', serif;
  color: #a0706a;
  text-align: center;
  font-size: 1.3em;
}

p {
  line-height: 1.8;
  text-align: justify;
}
```

## Tracking Instagram Ads

*An observational data analysis — STATS 220 Project 2*

This report explores patterns in Instagram advertisements observed over several days. Each time an ad appeared, details were recorded including where it showed up, what it was advertising, how long it was watched, how relevant it felt, and whether it seemed connected to recent online activity.
```{r}
logged_data <- read_csv("https://docs.google.com/spreadsheets/d/1PmrFla9Xemw-RrC-M-KMJ4VhgqLrxjm-bHqcJMGmZNU/export?format=csv&gid=736675154")

latest_data <- logged_data %>%
  rename(
    timestamp        = 1,
    location         = 2,
    category         = 3,
    seconds_watched  = 4,
    relevance        = 5,
    related_activity = 6
  )
```
```{r}
num_obs <- latest_data$seconds_watched %>% length()
mean_seconds <- latest_data$seconds_watched %>% mean() %>% round(1)
mean_relevance <- latest_data$relevance %>% mean() %>% round(1)
max_seconds <- latest_data$seconds_watched %>% max()
```

`r paste0("A total of ", num_obs, " Instagram ads were observed. On average, ads were watched for ", mean_seconds, " seconds, with the longest observation lasting ", max_seconds, " seconds. The mean relevance rating was ", mean_relevance, " out of 5, suggesting a moderate level of personalisation.")`

---

### Where Are Ads Appearing?

Ads were observed across different sections of Instagram including the Feed, Reels, Stories, and Explore page. The chart below shows which locations generated the most ad impressions during the observation period.
```{r fig.width=7, fig.height=4, fig.align='center'}
latest_data %>%
  ggplot() +
  geom_bar(aes(x = location), fill = "#7b4f6e") +
  labs(
    title = "Where Were Ads Seen?",
    x = "Instagram Location",
    y = "Number of Ads",
    caption = "Source: Instagram Ad Observation Log"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, family = "serif", size = 14, face = "bold"),
    axis.text = element_text(size = 11),
    plot.caption = element_text(color = "grey60")
  )
```

---

### What Types of Ads Are Showing Up?

Each ad was categorised by its content type. The chart below breaks down the spread of ad categories, giving insight into what kinds of products and services Instagram is promoting most frequently.
```{r fig.width=7, fig.height=4, fig.align='center'}
latest_data %>%
  ggplot() +
  geom_bar(aes(x = category), fill = "#c47c5a") +
  labs(
    title = "Ad Categories Observed",
    x = "Category",
    y = "Number of Ads",
    caption = "Source: Instagram Ad Observation Log"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, family = "serif", size = 14, face = "bold"),
    axis.text = element_text(size = 11),
    plot.caption = element_text(color = "grey60")
  )
```

---

`r paste0("Overall, the data suggests that Instagram's ad delivery is moderately targeted — with a mean relevance score of ", mean_relevance, " out of 5 across ", num_obs, " observations. Further data collection may reveal stronger patterns over time.")`
